Verifying synchronous distributed algorithms using IVy

### 2018-08-12 paper/paper.tex
- page 1, introductory paragraph: "not to be satisfied" can be replaced by

In Ivy, the entity ``calling'' the algorithm in different state configurations is called the ``environment''. The environment conceptually represents the final users of the algorithm. An algorithm or protocol is \textit{correct} or \textit{safe} if it cannot be called by the environment in a state configuration that causes some pre-defined properties (assertions, invariants) not to be satisfied. IVy supports verification of systems that have multiple methods (\textit{actions}) exported to the environment. For example to verify servers that specify connection and disconnection algorithms. This can be thought of as proving inductiveness of two independent algorithms with respect to the same invariants and system-state.

>>>>

In Ivy, the entity ``calling'' the algorithm in different state configurations is called the ``environment''. The environment conceptually represents the final users of the algorithm. An algorithm or protocol is \textit{correct} or \textit{safe} if it cannot be called by the environment in a state configuration that causes some pre-defined properties (assertions, invariants) to be violated. IVy supports verification of systems that have multiple methods (\textit{actions}) exported to the environment. For example to verify servers that specify connection and disconnection algorithms. This can be thought of as proving inductiveness of two independent algorithms with respect to the same invariants and system-state.
